Eliminating object prior-bias from sparse-projection tomographic reconstructions

### 2021-09-20 paper/changes.tex
updated changes with some reformatting and updated post_tci in two places

This paper was submitted earlier, and out of the three reviewers, two of them had pronounced this as ``publish unaltered'' and one reviewer (R1) did not recommend resubmission. The handling Editor has encouraged a resubmission of this paper taking into account the comments of R1.  We thank all reviewers for their remarks and in this document, we explain the steps we have taken to address the reviews received in our previous submission to TCI. R1 has these concerns and we quote these
\begin{quote}
  \textcolor{blue}{The authors have spent considerable effort in revising the
  manuscript and addressing the concerns of the reviewers. I would
  like to thank the authors for their effort. I believe the manuscript
  has improved because of these revisions, especially in the structure
  of the paper and the discussion of related work. Unfortunately, some
  of my main concerns with regards to the experiments, the accuracy of
  the proposed method, and the presentation of the findings remain
  present in the revised manuscript. In some cases the revisions have
  even increased my concerns about certain aspects. Mainly, the
  included experiments still do not clearly show that the proposed
  method improves upon existing ‘simple’ prior-based methods, and the
  new results even show that there is evidence that FDK is more
  accurate than the proposed method exactly in the region that changed}
  \end{quote}

\begin{itemize}
\item \textbf{In particular, we address the following main concern of the reviewer below.}\\

    \textcolor{blue}{Note that the total
variation minimization results are much better than the l1-ls results that the authors show in the
paper.}\\

The Reviewer has taken pains in showing how the Total-Variation method
is better than our earlier Compressed Sensing plus spatially-varying
prior-based reconstruction. In some cases FDK is more accurate.

This is correct for the dataset shown, and we accept this to be true.

  That said, the goal of our previous and curent work is to provide a
  technique that can improve upon a chosen baseline reconstruction
  when measurements are extremely sparse.  One may choose any baseline
  reconstruction for pedagogical, historical, or commercial reasons,
  and given that, our key question is-- is there a way to improve?

  Nevertheless, after noting reviewer's comments, we conducted further
  analysis and observed that TV is indeed better suited as a baseline
  reconstruction method for our datasets and our subsampling
  choices. Hence, our current paper presents all results using TV
  regularization coupled with spatially-varying technique, and
  demonstrates its benefits over TV-only and backprojection-only
  methods.  We have eliminated our previous implicit claim that the CS
  based scheme is optimal for the dataset provided.

  As far as FDK is concerned, the current results indeed show the
  superiority of the TV-based scheme (as also noted by the reviewer).
  \clearpage
\item \textbf{Other comments given by Reviewer R1 and the handling editor}

@@

   We have now discussed the difficulties in using deep-learning
   techniques for the current problem in Sec.~7C of our paper. We also
   describe them here below.

@@

\item \textcolor{blue}{Why did the authors not choose the standard
  settings for SSIM?...I don’t understand the reason given for not
  including RMSE: the values don’t have to be optimized again -- you
  could just optimize for SSIM but at least still report RMSE
  comparisons.}\\

  In our experiments, we observed that for a given dataset and a set of projection measurements, the intensity span of histograms of reconstructed volumes differ across various methods and solvers. Hence, we choose to focus on preserving the structures on our reconstructions, and not rely on the absolute intensity values alone. Hence, we choose SSIM with a higher weightage to structure-preservation. For our record, we have computed RMSE values as well and they are presented here in Tables~\ref{table:potato_rmse} and~\ref{table:sprouts_rmse}.

@@

\end{itemize}

>>>>

This paper was submitted earlier, and out of the three reviewers, two
of them had pronounced this as ``publish unaltered'' and one reviewer
(R1) did not recommend resubmission. The handling Editor has
encouraged a resubmission of this paper taking into account the
comments of R1.  We thank all reviewers for their remarks and in this
document, we explain the steps we have taken to address the reviews
received in our previous submission to TCI. R1 makes the following
comments, and we quote excerpts in blue here:
\begin{quote}
  \textcolor{blue}{The authors have spent considerable effort in revising the
  manuscript and addressing the concerns of the reviewers. I would
  like to thank the authors for their effort. I believe the manuscript
  has improved because of these revisions, especially in the structure
  of the paper and the discussion of related work. Unfortunately, some
  of my main concerns with regards to the experiments, the accuracy of
  the proposed method, and the presentation of the findings remain
  present in the revised manuscript. In some cases the revisions have
  even increased my concerns about certain aspects. Mainly, the
  included experiments still do not clearly show that the proposed
  method improves upon existing ‘simple’ prior-based methods
%% , and the
%%   new results even show that there is evidence that FDK is more
%%   accurate than the proposed method exactly in the region that changed
  }
  \end{quote}

The simpler method is based on the well-known ``Total Variation''. 
In particular, we address the following main concern of the reviewer 
\begin{quote}  
    \textcolor{blue}{Note that the total
variation minimization results are much better than the l1-ls results that the authors show in the
paper}
\end{quote}

    by rewriting the paper considerably.  We believe the paper
    addresses this (correct) stinging criticism of R1.  In fact R1 has taken
    pains in showing how the Total-Variation method (and sometimes
    FDK) is better than our earlier Compressed Sensing plus
    spatially-varying prior-based reconstruction, and we gratefully
    acknowledge the same.

Again, this is correct for the dataset shown, and we accept this to be
true.

  We re-wrote our code and upon further analysis observed that TV is
  indeed better suited as a baseline reconstruction method for our
  datasets and our subsampling choices. Hence, our current paper
  presents all results using TV regularization coupled with
  spatially-varying technique, and demonstrates  benefits over
  TV-only and backprojection-only methods.  \emph{We have eliminated our
  previous implicit claim that the CS based scheme is optimal for the
  dataset provided. }

  As far as FDK is concerned, the current results indeed show the
  superiority of the TV-based scheme (as also noted by the reviewer).

    That said, the goal of our previous and curent work is to provide
    a technique that can improve upon a chosen baseline reconstruction
    when measurements are extremely sparse.  One may choose any
    baseline reconstruction (including an inferior -- for this dataset
    -- Compressed sensing prior) for pedagogical, historical, or
    commercial reasons, and given that, our key question is -- is
    there a way to improve?  The spatially-varying method of
    moderating the prior settles this question.

We also take this opportunity to address other comments given by R1
and the handling editor.

@@

   We accept this point, and have now discussed the difficulties in
   using deep-learning techniques for the current problem in Sec.~7C
   of our paper. We also describe them here below.

\textcolor{red}{Comment from Sharat:  Since the material is in the text, there is no need to mention it here.}

@@

\item \textcolor{blue}{Why did the authors not choose the standard
  settings for SSIM?...I don’t understand the reason given for not
  including RMSE: the values don’t have to be optimized again -- you
  could just optimize for SSIM but at least still report RMSE
  comparisons.}

  The reason for not reporting RMSE stems from the optimization
  process. The optimization routine we use transforms the
  reconstruction to a different space.  That is, in our experiments,
  we observed that for a given dataset and a set of projection
  measurements, the intensity span of histograms of reconstructed
  volumes differ across various methods and solvers. As a result, the
  RMSE values are not particularly useful.  We provide the numbers
  here to show the improvement trend but we believe it does not serve
  the interest of the community to report these.

  For the same reason, the standard setting of SSIM in matlab (for
  instance) emphasizes the intensity. We found that even when the
  quality of reconstruction is acceptable visually, the SSIM values
  were not acceptable.  We choose
  to focus on preserving the structures on our reconstructions, and
  not rely on the absolute intensity values alone. Hence, we choose
  SSIM with a higher weightage to structure-preservation. For our
  record, we have computed RMSE values as well and they are presented
  here in Tables~\ref{table:potato_rmse} and~\ref{table:sprouts_rmse}.

@@

### 2021-09-20 paper/post_tci.tex
updated changes with some reformatting and updated post_tci in two places

In summary, the key contributions are
\begin{itemize}
\item We create new 3D biological datasets (Section~\ref{sec:datasets}) and
  present results on real cone-beam projections. Our datasets and code
  will be made available to the community.
  \item We design a weights-map
    to depict the location and strength of new changes in the test at
    every voxel. A novel algorithm is presented to build this map from
    sub-sampled measurements of the test and a set of high quality
    templates. Once the weights-map is built, it is used for accurate
    reconstruction of those changes in the test that are absent in all
    of the templates. Results appear in
    Section~\ref{sec:results_spatially_varying_prior}.
  \item We show the efficacy of our results in a real-life medical
    longitudinal study with data obtained in a clinical setting from
    a live teaching and
    research hospital.
\end{itemize}

%-------------------------------Dataset----------------------------
\section{Datasets}
\label{sec:datasets}
In this section, we present details of the biological and medical
datasets created and used for this work. For the first two datasets
namely, Potato and Okra, the raw measurements and  corresponding
parameters for cone-beam imaging model are available to us.
Hence all reconstructions on these datasets were performed directly
from real projection measurements. For the other two datasets namely, Sprouts and
Liver, the raw measurements and the parameters of imaging
model were not available to us (due to propriety concerns) and hence
only reconstructed volumes of real data were at hand; we therefore
generated measurements from these datasets assuming a circular
cone-beam imaging model for 3D and a parallel-beam imaging model for
2D.

@@

In this section, we first illustrate the advantage of using multiple types of eigenspaces for the computation of weights map, and then present reconstruction results on all datasets. For quantitative evaluation, we compute the Structural Similarity Index Metric (SSIM)~\cite{ssim}. Here, we assign higher importance to the preservation of structure in a reconstruction by assigning the following weights to structure, contrast and intensity respectively: $0.7,0.2,0.1$.

>>>>

In summary, the key contributions are
\begin{itemize}
\item We create new 3D biological datasets (Section~\ref{sec:datasets}) and
  present results on real cone-beam projections. Our datasets and code
  will be made available to the community.
  \item We design a weights-map
    to depict the location and strength of new changes in the test at
    every voxel. A novel algorithm is presented to build this map from
    sub-sampled measurements of the test and a set of high quality
    templates. Once the weights-map is built, it is used for accurate
    reconstruction of those changes in the test that are absent in all
    of the templates. Results appear in
    Section~\ref{sec:results_spatially_varying_prior}.
  \item We show the efficacy of our results in a real-life medical
    longitudinal study with data obtained in a clinical setting from
    a live teaching and
    research hospital.
\end{itemize}
While we demonstrate our results with a Total Variation regularization
prior, this work provides a technique that can improve upon any chosen
baseline reconstruction when measurements are extremely sparse.

%-------------------------------Dataset----------------------------
\section{Datasets}
\label{sec:datasets}
In this section, we present details of the biological and medical
datasets created and used for this work. For the first two datasets
namely, Potato and Okra, the raw measurements and corresponding
parameters for cone-beam imaging model are available to us.  Hence all
reconstructions on these datasets were performed directly from real
projection measurements. These datasets are ``Type A'' datasets in the
description below.  For the other two datasets (Type B), namely,
Sprouts and Liver, the raw measurements and the parameters of imaging
model were not available to us (due to propriety concerns) and hence
only reconstructed volumes of real data were at hand; we therefore
generated measurements from these datasets assuming a circular
cone-beam imaging model for 3D and a parallel-beam imaging model for
2D.

@@

In this section, we first illustrate the advantage of using multiple
types of eigenspaces for the computation of weights map, and then
present reconstruction results on all datasets. For quantitative
evaluation, we compute the Structural Similarity Index Metric
(SSIM)~\cite{ssim}. Here, we assign higher importance to the
preservation of structure in a reconstruction by assigning the
following weights to structure, contrast and intensity respectively:
$0.7,0.2,0.1$. The reason for emphasizing the structure with an
exponent of 0.7 steps from the optimization process since the
intensity span and, in general, the histogram of reconstructed volumes
differ across various methods and solvers.
